Hospitalizations for psychiatric conditions among adolescents during the COVID-19 pandemic

### 2021-11-09 psy_peds_3.Rmd
qc added to check which are the codes used in each site

listOfPackages <- c("tidyverse", "RColorBrewer", "knitr", "kableExtra", "tsModel", "gridExtra", "dplyr")
paket(listOfPackages)
```

@@

@@

# add the site id as column for each of the output data frames
count_icd$siteid = site 
patient_count_psy_period_psy$siteid = site 
patient_count_psy_period_psy_clear$siteid = site 
bootstrapped_coefficients_df$siteid = site 
bootstrapped_fitted_df$siteid = site 
perc_disorder_group$siteid = site 
patients_hospitalized_agg_sex_perc$siteid = site 
table1$siteid = site

save( count_icd,
      patient_count_psy_period_psy,
      patient_count_psy_period_psy_clear,
      bootstrapped_coefficients_df,
      bootstrapped_fitted_df,
      perc_disorder_group,
      patients_hospitalized_agg_sex_perc,
      table1,
      length_hospitalisation_values,
      file = paste0("output/peds_psy_aggResults_", site, ".RData"))
```

>>>>

listOfPackages <- c("tidyverse", "RColorBrewer", "knitr", "kableExtra", "tsModel", "gridExtra", "dplyr", "lubridate")
paket(listOfPackages)
```

@@

#### QC step: do a summary of the mental health ICD codes present in each site
As output we will generate a table with: the number of observations per code, number of patients diagnosed with each code and the date range in which the code was used.

```{r}
#filter the whole dataset to only mental codes
mental_codes_qc <- all_codes_ado %>% 
  filter( concept_code %in% mentalHealthCodes$concept_code )

mental_codes_qc_output <- mental_codes_qc %>%
  group_by( concept_code ) %>%
  dplyr::summarise( distinct_patients = ifelse(length(unique(patient_num)) > obfuscation | isFALSE(obfuscation),
                               length(unique(patient_num)), 
                               0.5),
                    distinct_observations = ifelse(length(patient_num) > obfuscation | isFALSE(obfuscation),
                               length(patient_num), 
                               0.5),                           
                    min_date = min( dmy( calendar_date ) ), 
                    max_date = max( dmy( calendar_date ) ))%>% 
  arrange(desc(distinct_observations))

mental_codes_qc_output <- left_join( mental_codes_qc_output, icdCodes, by=c("concept_code"= "ICD10_Code")) 
mental_codes_qc_output  <- mental_codes_qc_output[, c("disorder_group", "description", "concept_code", "distinct_patients", 
                                                    "distinct_observations", "min_date", "max_date")]

mental_codes_qc_output[1:10, ]
```

@@

# add the site id as column for each of the output data frames
mental_codes_qc_output$siteid = site 
count_icd$siteid = site 
patient_count_psy_period_psy$siteid = site 
patient_count_psy_period_psy_clear$siteid = site 
bootstrapped_coefficients_df$siteid = site 
bootstrapped_fitted_df$siteid = site 
perc_disorder_group$siteid = site 
patients_hospitalized_agg_sex_perc$siteid = site 
table1$siteid = site 
ratios_patients_with_without_psy$siteid = site

save( count_icd,
      mental_codes_qc_output,
      ratios_patients_with_without_psy,
      patient_count_psy_period_psy,
      patient_count_psy_period_psy_clear,
      bootstrapped_coefficients_df,
      bootstrapped_fitted_df,
      perc_disorder_group,
      patients_hospitalized_agg_sex_perc,
      table1,
      length_hospitalisation_values,
      file = paste0("output/peds_psy_aggResults_", site, ".RData"))
```
